Ecosystem carbon balance in the Hawaiian Islands under different scenarios of future climate and land use change

### 2020-07-23 Manuscript/HI_Model_ms.Rmd
edited Rmd manuscript

## Methods
We used the Land Use and Carbon Scenario Simulator (LUCAS), an integrated landscape change and carbon gain-loss model, to project changes in ecosystem carbon balance for the seven main Hawaiian Islands under four scenarios of climate and land-use change. The landscape change portion of LUCAS is a state-and-transition model that applies a Monte Carlo approach to track the state type and age of each simulation cell in response to a pre-determined set of transitions [@daniel_state-and-transition_2016]. The carbon gain-loss portion of LUCAS tracks carbon stocks within each simulation cell over time as continuous state variables, as well as a pre-defined set of continuous flows specifying stock level rates of change over time [@daniel_integrating_2018]. The Hawai`i LUCAS model estimated the annual change in carbon stocks and fluxes in response to land use changes associated with urbanization, agricultural expansion and contraction, forest and agricultural harvesting, and wildland fire. We also estimated the impact of short- and long-term climate variability on net primary productivity and the turnover of dead organic matter [@sleeter_effects_2019].

@@

The study area encompassed the terrestrial portion of the seven main Hawaiian Islands, a total land area of 16,464 km^2^ (Figure 1). This land area was subdivided into a grid of 250 x 250 m simulation cells. Each simulation cell was assigned to one of 210 possible state types based on the unique combination of three moisture zones (dry, mesic, and wet; Figure S1), seven islands, and ten discrete land cover classes (Figure 1).

>>>>

## Methods
We used the Land Use and Carbon Scenario Simulator (LUCAS), an integrated landscape change and carbon gain-loss model, to project changes in ecosystem carbon balance for the seven main Hawaiian Islands under four scenarios of climate and land-use change. The landscape change portion of LUCAS is a state-and-transition model that applies a Monte Carlo approach to track the state type and age of each simulation cell in response to a pre-determined set of transitions [@daniel_state-and-transition_2016]. The carbon gain-loss portion tracks carbon stocks within each simulation cell over time as continuous state variables, along with a pre-defined set of continuous flows specifying stock level rates of change over time [@daniel_integrating_2018]. We parameterized the Hawai`i LUCAS model to estimate annual changes in carbon stocks and fluxes in response to land use, land use change, wildland fire, and long-term climate variability [@sleeter_effects_2019].

@@

We subdivided the terrestrial portion of the seven main Hawaiian Islands, a total land area of 16,464 km^2^, into a grid of 250 x 250 m simulation cells. Each simulation cell was assigned to one of 210 possible state types based on the unique combination of three moisture zones (dry, mesic, and wet; Figure S1), seven islands, and ten discrete land cover classes (Figure 1).
